---
title: "Bold Tweets"
output:
  html_notebook: default
  html_document: default
---

## Friday May 4, 2018 with all analysis
## Data cleaning
```{r}
congress = read.csv('more-data/all_w_IBM_50.csv')
# clean data - convert to numeric
congress[is.na(congress)] = 0
congress$gender = as.numeric(congress$gender)
congress$type = as.numeric(congress$type)
congress$party = as.numeric(congress$party)
congress
```

### Take rates of tag
```{r}
#round_ones = function(col){
#  col[col != 0] = 1
#  col
#}
#round_ones(congress$Joy)

congress$Sadness[congress$Sadness != 0] = 1
congress$Joy[congress$Joy != 0] = 1
congress$Tentative[congress$Tentative != 0] = 1
congress$Confident[congress$Confident != 0] = 1
congress$Analytical[congress$Analytical != 0] = 1
congress$Anger[congress$Anger != 0] = 1
congress$Fear[congress$Fear != 0] = 1
congress
```

## Old style analysis
* tweets viewed as all $y_i = ax_i + b$ with normally distributed error
* women more sad
* men more joyful
* women MAYBE more tentative
* women more analytical
* women more fearful
```{r}
women_tweets = congress[congress$gender == 1,]
men_tweets = congress[congress$gender == 2,]
t.test(women_tweets$Sadness, men_tweets$Sadness) #, var.equal = TRUE)
t.test(women_tweets$Joy, men_tweets$Joy)
t.test(women_tweets$Tentative, men_tweets$Tentative)
t.test(women_tweets$Analytical, men_tweets$Analytical)
t.test(women_tweets$Confident, men_tweets$Confident)
t.test(women_tweets$Fear, men_tweets$Fear)
t.test(women_tweets$Anger, men_tweets$Anger)
```

## Retweets, Favorites
* yes women also favorited when confident, not as much as men (nearly significant)

### visualize

```{r}
dep = congress$tweet_favorite_count
w_tweets = dep[congress$gender == 1]
g = split(congress, congress$gender)
wom = split(g$`1`, g$`1`$Confident) # women
men = split(g$`2`, g$`2`$Confident) # men
one = wom$`0` # not conf women
two = wom$`1` # conf women
three = men$`0` # not conf men
four = men$`1` # conf men
```

```{r}
f = function(dat){
  log(1+log(1+dat$tweet_favorite_count))#[dat$tweet_favorite_count>0]))
}
#congress$tweet_favorite_count>0
hist(f(congress), main='Favorites ~ Power Law', xlab='log log favorites')
barplot(c(mean(f(one)), mean(f(two)), mean(f(three)), mean(f(four))), names.arg=c('Women Neutral', 'Women Confident', 'Men Neutral', 'Men Confident'), main = 'Favorites vs. Confidence and Gender', ylab= 'log log favorite (mean)')

boxplot(f(one), f(two), f(three), f(four), ylab='log favorites', names = c('Women not conf', 'Women conf', 'Men not conf', 'Men conf'), main='Men more rewarded for confidence')
```


### formalism
* all are more favorited when confident
* men more so than women
```{r}
dep = f(congress)
mfav10 = lm(dep ~ congress$Confident + congress$gender) # both effects significant, women are favorited more
mfavint0 = lm(dep ~ congress$Confident * congress$gender)
anova(mfav10, mfavint0)
```


* NOT SIG WHEN TAKE OUT ZERO-FAVORITES - maybe something to do with retweet status?
```{r}
f = function(dat){
  log(1+log(1+dat$tweet_favorite_count[dat$tweet_favorite_count>0]))
}
#dep = log(1+congress$tweet_favorite_count)
fact = congress$tweet_favorite_count > 0

dep = f(congress)
head(congress)
mfav0 = lm(dep ~ congress$Confident[fact]) # positive, significant
mfav1 = lm(dep ~ congress$Confident[fact] + congress$gender[fact]) # both effects significant, women are favorited more
mfavint = lm(dep ~ congress$Confident[fact] * congress$gender[fact])
summary(mfav0)
summary(mfav1)
summary(mfavint)
anova(mfav1, mfavint) # reject mfav1 at p~.05, means there is an interaction. NOT IF WE REMOVE ZERO-valued tweets!
```
* new new: mixed effect model
confidence not sig at all; everything is just individual variance.
```{r}
library(nlme)
colnames(congress)
head(congress)
m <- lme(tweet_retweet_count ~ Confident,
          random = ~1 | twitter, data=congress)
summary(m)
```


### Are the zero-favorited tweets outliers?
```{r}
#four$IBM_text[four$tweet_favorite_count==0]
5
```


## New analysis: aggregate first
* note: I'm *AM* doing the nonzero->1 trick with IBM scores.
* be careful if you run in a certain order the above; the following analysis might change.
```{r}
agged = aggregate(congress, by=list(congress$twitter), FUN=function(x) mean(as.numeric(x)))
                    #mean)
congress
agged
```
hi
```{r}
women = agged[agged$gender == 1,]
women
men = agged[agged$gender == 2,]
men
#agged$Anger[agged$Anger != 0]
```

### Gender diffs (or lack thereof) by plots
* Sadness, Joy, Analytical, Confident = not too sparse
* Tentative = borderline
* Fear, anger = too sparse
```{r}
measure = "Politician IBM score (mean)"
shapiro.test(women$Joy) # not normally distributed
shapiro.test(women$Tentative)
hist(women$Sadness)
hist(women$Joy, xlab=measure, main='Joy - Approximately normal (p > .05)')
hist(women$Tentative, xlab=measure, main='Tentative - Not approx. normal (p < 1e-05)')
hist(women$Analytical)
hist(women$Confident)
hist(women$Fear)
hist(women$Anger)
```

### agged women against men plots
```{r}
indep_col_1 = rgb(0,0,1,1/4)
indep_col_2 = rgb(1,0,0,1/4)
depw = women$Analytical
depm = men$Analytical
hist(depw, col=indep_col_1, main='Women as or more Analytical', xlab=measure)
hist(depm, col=indep_col_2, add=T)
legend1 = "Analytical - women"
legend2 = "Analytical - men"
legend(.25, 30, legend=c(legend1, legend2),
       col=c(indep_col_1, indep_col_2), lty=1, lwd=10, cex=0.8)
d = data.frame(women=depw, men=depm[1:107])
boxplot(d, main='Women as or more Analytical', ylab=measure)
#stripchart(d,
#            vertical = TRUE, #method = "jitter", 
#            pch = 21, col = "maroon", bg = "bisque",
#            add = TRUE) 
#hist(women$Sadness, col=indep_col_1)
#hist(men$Sadness, col=indep_col_2, add=T)
#plot(p1, col='blue')
```
```{r}
d = data.frame(women_sad=women$Sadness, men_sad=men$Sadness[1:107], women_joy = women$Joy, men_joy = men$Joy[1:107])
boxplot(d, main='Women not more \"agreeable\"', ylab=measure, names = c("Women sad", "Men sad", "Women joy", "Men joy"))
d2 = data.frame(women_conf=women$Confident, men_conf = men$Confident[1:107], women_analytic=women$Analytical, men_analytic = men$Analytical[1:107])
boxplot(d2, main='Women as or more \"forceful\"', ylab=measure, names = c("Women conf", "Men conf", "Women analytical", "Men analytical"))
```

### Numerical conclusions, correspond to above visuals
* women more sad
* Men more joy
* women more analytical
* can get confidence interval on women's CONFIDENCE relative to men
* Women likely more fearful
* Similar anger
```{r}

t.test(women$Sadness, men$Sadness) #, var.equal = TRUE)
t.test(women$Joy, men$Joy)
t.test(women$Tentative, men$Tentative)
t.test(women$Analytical, men$Analytical)
x = t.test(women$Confident, men$Confident)
x
x$conf.int
x$estimate
# t.test(women$Confident, men$Confident, alternative = 'greater')
t.test(women$Fear, men$Fear)
t.test(women$Anger, men$Anger)
```

### Robustness
* fuller models into party, age.

* sad women remains stat sig even with party; some small evidence for involving the fuller model with an additive party or interacted party.
```{r}
msad1 = lm(agged$Sadness ~ agged$gender)
msad11 = lm(agged$Sadness ~ agged$party)
msad111 = lm(agged$Sadness ~ agged$age)
#plot(msad111)
#plot(agged$age, agged$Sadness)
#abline(msad111)

summary(msad1)
# model involving party:
msad2 = lm(agged$Sadness ~ agged$gender + agged$party)
summary(msad2)
anova(msad1, msad2)
```

* Men more joy is not robust to party. Republicans are more joyful given Trump, naturally.
* age not needed
```{r}
mjoy1 = lm(agged$Joy ~ agged$gender)
mjoy2 = lm(agged$Joy ~ agged$gender + agged$party)
mjoy3 = lm(agged$Joy ~ agged$gender + agged$party + agged$age)
summary(mjoy1)
summary(mjoy2)
summary(mjoy3)
anova(mjoy1, mjoy2)
anova(mjoy2, mjoy3)
```

* _Democrats_ more analytical, women still stat significant
* interactions not needed, age not needed.
```{r}
mAnalytical1 = lm(agged$Analytical ~ agged$gender)
mAnalytical2 = lm(agged$Analytical ~ agged$gender + agged$party)
mAnalytical3 = lm(agged$Analytical ~ agged$gender * agged$party)
mAnalytical4 = lm(agged$Analytical ~ agged$gender + agged$party + agged$age)
summary(mAnalytical1)
summary(mAnalytical2)
anova(mAnalytical1, mAnalytical2)
# interactions not needed.
anova(mAnalytical2, mAnalytical3)
anova(mAnalytical2, mAnalytical4)
```

* party does not help explain the non-result of confidence.
```{r}
mConfident0 = lm(agged$Confident ~ agged$party)
mConfident1 = lm(agged$Confident ~ agged$gender)
mConfident2 = lm(agged$Confident ~ agged$gender + agged$party)
mConfident3 = lm(agged$Confident ~ agged$gender * agged$party)
mConfident4 = lm(agged$Confident ~ agged$gender + agged$party + agged$age)
summary(mConfident0)
summary(mConfident1)
summary(mConfident2)
anova(mConfident1, mConfident2)
# interactions not needed.
anova(mConfident2, mConfident3)
anova(mConfident2, mConfident4)
# HELLO, SAVE!
```


